%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Alex Quach} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:14073602099}{+1 (407) 360-2099}
    $|$
    \faAt \hspace{.5pt} \href{mailto:alexhq1000@gmail.com}{alexhq1000@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/alexhquach/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/alexquach}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://thequach.com}{Website}
    % $|$
    % \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Bogazici+University+North+Campus/@41.0863067,29.0441352,15z/data=!4m5!3m4!1s0x0:0x9d2497b07c8edb2f!8m2!3d41.0863067!4d29.0441352}{Istanbul, Turkey}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Massachusetts Institute of Technology
      }{Cambridge, MA, USA}
      {S.B. in Computer Science and Engineering (6-3) |   \textbf{GPA: 5.00/5.00}}{Sep 2019 \textbf{--} May 2023}
      {S.M. in Computer Science and Engineering (6-3)
      }{Jun 2023 \textbf{--} May 2024}
        \resumeItemListStart
            \resumeItem{\textbf{Relevant coursework:} (Advanced) Algorithms, Machine Learning, Computer Vision, Natural Language Processing, TinyML and Efficient Deep Learning, Multiagent Learning, Embedded Systems, Probability and Random Variables, Linear Algebra, Software Construction}
        \resumeItemListEnd
    
    % \resumeSubheading
      % {Kocaeli Science High School
      % \normalfont{(Admission rate: 0.85\%)}
      % }{Kocaeli, Turkey}
      % {High School Diploma;   \textbf{GPA: 97.03/100}}{Sep 2014 \textbf{--} Jun 2018}
    
  \resumeSubHeadingListEnd





%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {MIT Computer Science and Artificial Intelligence Lab (CSAIL)}{Cambridge, MA, USA}
      {Graduate Researcher \textnormal{- under the supervision of Prof. Daniela Rus (Distributed Robotics Lab)}}{Jun 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Demonstrating sim2real generalizability of end-to-end flight control using liquid neural networks. Training models with synthetic data generated by Neural Radiance Fields (NeRFs) and Gaussian Splatting.}
            \resumeItem{Designing novel robot training pipeline: incorporating dynamics from physics-based simulator; collecting photorealistic drone-POV images from gaussian splatting neural models; and showcasing trained model's real-world flight performance on quadrotor drones.}


        \resumeItemListEnd
    
    \vspace{8pt}
    
    \resumeSubheading
      {MIT.nano}{Cambridge, MA, USA}
      {Undergraduate Researcher \textnormal{- under the supervision of Prof. Farnaz Niroui (Tiny Lab)}}{Jan 2023 \textbf{--} May 2023}
      \resumeItemListStart
          \resumeItem{Assisted with the fabrication and characterization of nano-strained WS$e_2$, enclosured with hBN, using self-assembled monolayers, electron beam lithography, atomic force microscopy, cryogenic microscopy, atomic layer deposition, and thermal stressing. This constituted research towards the development of mechanically tunable, nanoscale optoelectrical devices.}
          \resumeItem{Developed Python code for identification of peaks (lorentz and centroid fitting) and quantification of strain from collected hyperspectral photoluminescence and raman spectroscopy data.}
        \resumeItemListEnd

        \vspace{8pt}

        \resumeSubheading
      {Broad Institute of MIT and Harvard}{Cambridge, MA, USA}
      {Undergraduate Researcher \textnormal{- under the supervision of Dr. Juan Caicedo}}{Sep 2021 \textbf{--} Dec 2022}
        \resumeItemListStart
          \resumeItem{Combined self-supervised contrastive learning (DINO) with normalizing flows to create a causal generative model for cellular images. This method allows for the generation of counterfactual images.}
          \resumeItem{Applied generative style transfer to correct for batch effects (inevitable technical noise) in cellular imaging}
        \resumeItemListEnd

        \vspace{8pt}

      \resumeSubheading
        {MIT Computer Science and Artificial Intelligence Lab (CSAIL)}{Cambridge, MA, USA}
        {Undergraduate Researcher \textnormal{- under the supervision of Prof. Julie Shah (Interactive Robotics Lab)}}{Nov 2020 \textbf{--} May 2021}
          \resumeItemListStart
              \resumeItem{Worked towards more interpretable neural network architectures by embedding prototypical data examples within the networks. Applied prototypical networks to demonstrate generalizability with domain adaptation task of MNIST / SVHN digit classification.}
          \resumeItemListEnd
      
      \vspace{8pt}

        \resumeSubheading
      {MIT Quest for Intelligence}{Cambridge, MA, USA}
      {Undergraduate Researcher}{Oct 2019 \textbf{--} May 2020}
        \resumeItemListStart
            \resumeItem{Implemented linear regression, Varmax, and LSTM time-series models to create temperature response simulator to model temperature response of MIT buildings to HVAC controls. Leveraged this model to reduce MIT Facility's greenhouse gas emissions by utilizing cleaner energy grid hours.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

  \section{Publications}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
      Wolfgang M. Pernice, Michael Doron, \textbf{Alex Quach}, Aditya Pratapa, Sultan Kenjeyev, Nicholas De Veaux, Michio Hirano, Juan C. Caicedo; ”Out of Distribution Generalization via Interventional Style Transfer in Single-Cell Microscopy,” Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR) Workshops, 2023, pp. 4326-4335
      }}
      \resumeSubHeadingListEnd


%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Plumerai}{Amsterdam, Netherlands}
      {Software Engineer Intern}{Jun 2022 \textbf{--} Aug 2022}
        \resumeItemListStart
            \resumeItem{Expanded the capabilities of TinyML person-tracking neural network that runs on Cortex M microcontroller (32K flash). Achieved 54\% improvement in person reidentification task by incorporated learned feature embeddings and 326\% speedup in video inference pipeline with multiprocessing. }
        \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{Redmond, WA, USA}
      {Data Science Intern | Responsible AI Tooling Team (Remote)}{Jun 2021 \textbf{--} Aug 2021}
        \resumeItemListStart
            \resumeItem{Developed specifications and implemented statistical uncertainty quantification for 10+ performance / fairness metrics, which were downstreamed into Azure and open-source offerings.}
            \resumeItem{Contributed to open-source software community, \textit{Fairlearn}, and wrote unit and end-to-end tests in Pytest, Jest, and Cypress.}
        \resumeItemListEnd

    \vspace{-16pt}
    
    \resumeSubheading
      {}{}
      {Product Manager Intern | Azure Machine Learning Team (Remote)}{Jun 2020 \textbf{--} Aug 2020}
      \resumeItemListStart
      \resumeItem{Drove end-to-end VSCode integration with AzureML compute across 5 engineering teams to allow seamless access to AzureML compute machines from VSCode extension and Github Codespaces access from AzureML web interface.}
      \resumeItem{Conducted customer interviews with internal and external customers, developed bash scripts for demostrating MVP use-case, and delivered specifications for software engineers teams to implement.}
    \resumeItemListEnd

    \vspace{-16pt}
    
    \resumeSubheading
      {}{}
      {Explore (SWE + PM) Intern | Azure Stack Team }{Jun 2019 \textbf{--} Aug 2019}
      \resumeItemListStart
            \resumeItem{Streamlined and visualized performance metrics across production builds by creating a Release Dashboard to
            enable data-driven decisions for Azure Stack releases.}
        \resumeItemListEnd
      
    
    \resumeSubheading
      {Botkeeper}{Boston, MA, USA}
      {ML Engineer Intern}{Sep 2020 \textbf{--} Dec 2020, part-time}
        \resumeItemListStart
            \resumeItem{Trained, integrated, and deployed NLP model to automate vendor classification for Acccounts Payable (AP) transactions. Optimized training pipeline to reduce monthly training time by 55\% (down from 9 days).}
        \resumeItemListEnd
      
        \vspace{-16pt}
    
        \resumeSubheading
        {}{}
      {Software Engineer Intern}{Jan 2020 \textbf{--} Feb 2020}
        \resumeItemListStart
            \resumeItem{Pioneered Quality Assurance service to improve accuracy of Accounts Payable Ledger by detecting human bookkeepers' errors with daily reports generated in Google Sheets. Autonomously identified and generated report of 9,617 accounting variances from 95 clients totaling over
            \$1.88 million on its first run.}
        \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Teaching \& Service}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{MIT Global Teaching Labs (Bahrain): }{Will teach robotics/electronics with an emphasis on wearable devices for university and high school students in Bahrain. (January 2024)} \\ \vspace{3pt}
        \textbf{MIT Global Teaching Labs (South Africa and Botswana): }{Workshop teaching robotics and machine learning for high school students in South Africa and Botswana. (January 2023)} \\ \vspace{3pt}
        \textbf{6.004 Computation Structures LA }{(Fall 2022)} \\ \vspace{3pt}
        \textbf{MIT School of Engineering Dean's Action Group on Social and Ethical Responsibilities of Computing }{(Fall 2020 - Spring 2021)} \\ \vspace{3pt}
        
  
    }}
  \resumeSubHeadingListEnd

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Eric and Wendy Schmidt Center Research and Innovation Scholar}{ (2021)} \\ \vspace{3pt}
        \textbf{MIT College of Computing Social and Ethical Responsibilities of Computing (SERC) Scholar}{ (2021)} \\ \vspace{3pt}
        \textbf{MIT Sandbox Innovation Fund Seed Grant}{ (2021)} \\ \vspace{3pt}
        \textbf{Glasswing Ventures Ignite Fellowship}{ (2020)} \\ \vspace{3pt}

        \textbf{FIRST Tech Challenge World Championship Inspire Award:}{ Highest award in FIRST Tech Challenge robotics competition: given to 2 teams out of 5,000 teams. (2018)} \\ \vspace{3pt}

        \textbf{US Presidential Scholar Semifinalist:}{ Awarded to about 800 high school seniors out of the entire country. (2018)} \\ \vspace{3pt}
  
    }}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ Python, TypeScript, C/C++, Java, R} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Linux, Kubernetes, Next.js, MySQL, MongoDB, Git, Docker, Amazon Web Services, Blender } \\ \vspace{3pt}

        \textbf{Libraries:}{ PyTorch, Keras, TensorFlow, OpenCV, Scikit-Learn, NumPy, Pandas, Matplotlib, Seaborn} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

% \section{Projects}
    % \vspace{3pt}
    % \resumeSubHeadingListStart
      
      % \resumeProjectHeading
        % {\textbf{Filters and Fractals} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch.}
            % \resumeItem{Added recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle in PPM format.}
          % \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{Chess Bot} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move.}
            % \resumeItem{Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
          % \resumeItemListEnd
      
      % \resumeProjectHeading
        % {\textbf{CMPE 250 Projects} $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
          % \resumeItemListStart
            % \resumeItem{Five Java projects assigned for the Data Structures and Algorithms (CMPE 250) course in the Fall 2021-22 semester.}
            % \resumeItem{These projects apply DS\&A concepts such as discrete-event simulation (DES) using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree (MST), Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
          % \resumeItemListEnd
      
    % \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
